### 2023-10-09 README.Rmd
added first choice rule and changed shareofpref to marksim

<li><code>shareofpref</code>: provides you the aggregated share of
preference, including the standard error, as well as the lower and upper confidence interval, which is
calculated according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$ (Orme, 2020, p. 94).</li>

>>>>

<li><code>marksim</code>: runs market simulations (either share of preference or first choice rule), including the standard error, as well as the lower and upper confidence interval, which is
calculated according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$ (Orme, 2020, p. 94).</li>
